### 2017-01-28 manuscript.rmd
now parse species names

		while( NA %in% new_age ) {
			x = sapply( 
				age,
				function( i ){
					rnorm( 1, mean = i, sd = ( sd_fraction * i ) )
				}
			)

@@

	#' Add phylogenetic independent contrasts (PIC) with the tree and 
	#' character data in a treeio::treedata object
	#' 
	#' @param gene_trees_pic A list of phylogenetic trees with pics
	#' as treeio::treedata objects 
	#' @return A tibble with combined data, including phylogenetic independent 
	#' contrasts, for internal nodes of all trees
	#' @export
	summarize_contrasts = function( gene_trees_pic ) {
		# Combine the @data slots across all trees. These have labels, node annotations,
		# expression data, contrast results, etc...
		all_nodes = 
			lapply( 
				gene_trees_pic, 
				function( nhx ){
					tags = nhx@data
					tags$gene = digest( nhx ) # Creates a  hash that is unique to each gene tree
					tags %<>% select( -( B ) ) # B has inconsistent types, remove it
					return( tags )
				}
			) %>%
			bind_rows()

@@

		# Create a subset that corresponds to nodes with contrasts. This excludes tips.
		# Also take the absolute value of the contrast, since we only consider magnitude.
		nodes_contrast = 
			all_nodes %>%
			filter( ! is.na( pic ) ) %>%
			mutate( pic = abs( pic ) ) %>%
			filter( ! is.na( D ) )

@@

	# Read the expression data for each species and combine into a single tibble
	expression = 
	lapply(
		expression_file_names, 
		read.table, 
		stringsAsFactors=FALSE, 
		header=TRUE
	) %>%
	bind_rows()

@@

	# Only retain strings that are trees
	lines = lines[ grepl( "^\\(", lines, perl = TRUE ) ]

	# Parse each string to a treeio::treedata object, adding a label column 
	# for node names
	gene_trees = mclapply(
		lines,
		function( x ){
			tree_tc = textConnection( x )
			tree = treeio::read.nhx( tree_tc )
			close( tree_tc )
			tree@data$label = c( tree@phylo$tip.label, tree@phylo$node.label )
			return( tree )
		}, mc.cores=cores
	)
```

>>>>

		# Keep trying until dates are coherent with tree structure
		# This is a ladder tree, so that means checking that they 
		# are still in ascending order
		while( NA %in% new_age ) {
			x = sapply( 
				age,
				function( i ){
					rnorm( 1, mean = i, sd = ( sd_fraction * i ) )
				}
			)

@@

	#' Add phylogenetic independent contrasts (PIC) with the tree and 
	#' character data in a treeio::treedata object
	#' 
	#' @param gene_trees_pic A list of phylogenetic trees with pics
	#' as treeio::treedata objects 
	#' @return A tibble with combined data, including phylogenetic independent 
	#' contrasts, for internal nodes of all trees
	#' @export
	summarize_contrasts = function( gene_trees_pic ) {
		# Combine the @data slots across all trees. These have labels, node annotations,
		# expression data, contrast results, etc...
		# Also take the absolute value of the contrast, since we only consider magnitude.
		all_nodes = 
			lapply( 
				gene_trees_pic, 
				function( nhx ){
					tags = nhx@data
					tags$gene = digest( nhx ) # Creates a  hash that is unique to each gene tree
					tags %<>% select( -( B ) ) # B has inconsistent types, remove it
					return( tags )
				}
			) %>%
			bind_rows() %>%
			mutate( pic = abs( pic ) )

@@

		# Create a subset that corresponds to nodes with contrasts. This excludes tips.
		nodes_contrast = 
			all_nodes %>%
			filter( ! is.na( pic ) ) %>%
			filter( ! is.na( D ) )

@@

@@

	# Isolate strings that are trees
	# These start with (
	tree_lines = lines[ grepl( "^\\(", lines, perl = TRUE ) ]

	# Parse each string to a treeio::treedata object, adding a label column 
	# for node names
	gene_trees = mclapply(
		tree_lines,
		function( x ){
			tree_tc = textConnection( x )
			tree = treeio::read.nhx( tree_tc )
			close( tree_tc )
			tree@data$label = c( tree@phylo$tip.label, tree@phylo$node.label )
			return( tree )
		}, mc.cores=cores
	)

	# Parse the tree annotations, these are lines that start with SEQ
	# These have the species names, which are not in the trees themselves
	tip_annotations = 
		lines[ grepl( "^SEQ", lines, perl = TRUE ) ] %>%	# Get lines that start with SEQ
		str_c( collapse="\n" ) %>%												# Combine them into one string
		read_delim( delim=" ", col_names = FALSE ) %>% 		# Read string as tibble
		select( 2, 8 ) %>%																# Select the columns with species and gene ID
		rename(  Ensembl.Gene.ID = X8 ) %>%
		rename(  species = X2 )

	# Read the expression data for each species and combine into a single tibble,
	# adding the species names from tip_annotations
	expression = 
		lapply(
			expression_file_names, 
			read.table, 
			stringsAsFactors=FALSE, 
			header=TRUE
		) %>%
		bind_rows() %>%
		left_join( tip_annotations, by="Ensembl.Gene.ID" )
